---
title: "Homework 7"
author: "Anthony Ferraro"
output:
  html_document:
    code_folding: hide
  pdf_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, comment = NA, fig.align = "center", out.width = "50%", warning = FALSE, message = FALSE)

library(tidyverse)
library(knitr)

theme_set(theme_minimal())

ggplot2::diamonds
```


#### Filtering the Diamonds Dataset
```{r}
filtered_diamonds <- diamonds %>%
  filter(color %in% c("D", "G", "J")) %>%
  filter(clarity %in% c("I1", "VS1", "IF"))

knitr::kable(filtered_diamonds %>%
               count(color, clarity) %>%
               arrange(desc(n))
             )
```

^[Question 1 Complete]



#### Plotting the Relationship Between Price and Carat
```{r}
ggplot(filtered_diamonds, aes(x = carat, y = price)) +
  geom_point(alpha = 0.5) +
  geom_smooth(method = "lm")
```
There seems to be a positive relationship between carat and price, which does make sense. Also, the relationship does seem to be linear. ^[Question 2 Complete]


#### Plotting the Relationship Between Price and Carat with Diamond Color
```{r}
ggplot(filtered_diamonds, aes(x = carat, y = price, color = color)) +
  geom_point(alpha = 0.5) +
  geom_smooth(method = "lm")
```

The relationship between carat and price is still positive and linear, however, it seems that some diamond colors have steeper price increases than others. ^[Question 3 Complete]


#### Plotting the Relationship Between Price and Carat with Diamond Color and Diamond Clarity
```{r}
ggplot(filtered_diamonds, aes(x = carat, y = price, color = color, shape = clarity, 
                              linetype = clarity)) +
  geom_point(alpha = 0.5) +
  geom_smooth(method = "lm")
```

I think that adding clarity in this way makes the graph harder to read as there are too many different shapes, colors, and line types on the graph. ^[Question 4 Complete]



#### Plotting the Relationship Between Price and Carat with Diamond Color and Clarity Faceted
```{r}
ggplot(filtered_diamonds, aes(x = carat, y = price)) +
  geom_point(alpha = 0.5) +
  geom_smooth(method = "lm") + 
  facet_grid(color ~ clarity)
```

Most of the carat vs. price relationships are still linear, although some look like they are almost exponential. The steepest relationship is between D color and IF clarity, which makes sense because they are the best for their respective categories. ^[Question 5 Complete]


#### Finding the Highest Price Per Carat Ratio
```{r}
knitr::kable(filtered_diamonds %>%
  mutate(price_per_carat = (price / carat)) %>%
  group_by(color, clarity) %>%
  summarize(avg_price_pc = mean(price_per_carat)) %>%
  arrange(desc(avg_price_pc))
)
  
```
The table does seem to agree with my plots, with the D color and IF clarity combination being the highest price per carat, and the G color and I1 clarity combination being the lowest price per carat.
^[Question 6 Complete]











