---
title: "Homework 7"
author: "Anthony Ferraro"
output:
  html_document:
    code_folding: hide
  pdf_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, comment = NA, fig.align = "center", out.width = "50%", warning = FALSE, message = FALSE)

library(tidyverse)
library(knitr)

theme_set(theme_minimal())

ggplot2::diamonds
```


#### Filtering the Diamonds Dataset
```{r}
filtered_diamonds <- diamonds %>%
  filter(color %in% c("D", "G", "J")) %>%
  filter(clarity %in% c("I1", "VS1", "IF"))

knitr::kable(filtered_diamonds %>%
               count(color, clarity) %>%
               arrange(desc(n))
             )
```

^[Question 1 Complete]



#### Plotting the Relationship Between Price and Carat
```{r}
ggplot(filtered_diamonds, aes(x = carat, y = price)) +
  geom_point(alpha = 0.5) +
  geom_smooth(method = "lm")
```
There seems to be a positive relationship between carat and price, which does make sense. Also, the relationship does seem to be linear. ^[Question 2 Complete]


#### Plotting the Relationship Between Price and Carat with Diamond Color
```{r}
ggplot(filtered_diamonds, aes(x = carat, y = price, color = color)) +
  geom_point(alpha = 0.5) +
  geom_smooth(method = "lm")
```

The relationship between carat and price is still positive and linear, however, it seems that some diamond colors have steeper price increases than others. ^[Question 3 Complete]











